\ifx\allfiles\undefined             %独立编译
\documentclass{article}
\usepackage{My_note}
\begin{document}
\title{}
\author{}
\date{}
%\else
%\chapter{}
\fi


\section{The dynamics of turbulence}

Two major questions:

\begin{itemize}
    \item How is the kinetic energy of the turbulence maintained?
    \item Why are vorticity and vortex stretching so important to the study of turbulence?
\end{itemize}

\subsection{Kinetic energy of the mean flow}

Mean flow energy: $\frac{1}{2}U_iU_i$

We already have

\begin{equation*}
    U_j\frac{\partial U_i}{\partial x_j}=\frac{\partial}{\partial x_j}\left(\frac{T_{ij}}{\rho}\right)
\end{equation*}

Multiply $U_i$ on both sides,

\begin{equation*}
    \rho U_j\frac{\partial}{\partial x_j}\left(\frac{1}{2}U_iU_i\right)=\frac{\partial}{\partial x_j}(T_{ij}U_i)-T_{ij}\frac{\partial U_i}{\partial x_j}
\end{equation*}

Note that

\begin{equation*}
    T_{ij}\frac{\partial U_i}{\partial x_j}=T_{ij}S_{ij}
\end{equation*}

by the definition of $S_{ij}$.

This term,

\begin{equation*}
    \frac{\partial}{\partial x_j}(T_{ij}U_i)
\end{equation*}

we can use the Gauss' theorem,

\begin{equation*}
    \int_V \frac{\partial}{\partial x_j}(T_{ij}U_i) dV=\int_S \frac{\partial}{\partial x_j}(T_{ij}U_i) ds
\end{equation*}

If we use a control volume, and on its surface $T_{ij}$ or $U_i$ is zero, then we know that the total amount of kinetic energy is changed by $T_{ij}S_{ij}$.

$T_{ij}S_{ij}$ is called the deformation work.

\textbf{Pure shear flow (omitted)}

\textbf{The effects of viscosity}

Substitute $T_{ij}$,

\begin{equation*}
    U_j\frac{\partial}{\partial x_j}\left(\frac{1}{2}U_iU_i\right)=\frac{\partial}{\partial x_j}\left(-\frac{P}{\rho}U_j+2\nu U_i S_{ij}-\overline{u_iu_j}U_i\right)+2\nu S_{ij}S_{ij}+\overline{u_iu_j}S_{ij}
\end{equation*}

\begin{itemize}
    \item $-\frac{\partial}{\partial x_j}\frac{P}{\rho}U_j$: pressure work
    \item $2\frac{\partial}{\partial x_j}\nu U_i S_{ij}$: transport of mean-flow energy by viscous stresses
    \item $-\frac{\partial}{\partial x_j}\overline{u_iu_j}U_i$: transport of mean-flow energy by Reynolds stresses
\end{itemize}

And the last two terms are negligible in most flows.

We define the representative velocity $\mathcal{u}$

\begin{equation*}
    \mathcal{u}^2=\frac{1}{3}\overline{u_i u_i}
\end{equation*}

\subsection{Kinetic energy of the turbulence}

The turbulent energy budget

\begin{equation*}
    \begin{aligned}
        U_j\frac{\partial}{\partial x_j}\left(\frac{1}{2}\overline{u_iu_i}\right)=&-\frac{\partial}{\partial x_j}\left(\frac{1}{\rho}\overline{u_jP}+\frac{1}{2}\overline{u_iu_iu_j}-2\nu\overline{u_i s_{ij}}\right)\\
        &-\overline{u_iu_j}S_{ij}-2\nu\overline{s_{ij}s_{ij}}
    \end{aligned}
\end{equation*}

The fluctuating rate of strain

\begin{equation*}
    s_{ij}=\frac{1}{2}\left(\frac{\partial u_i}{\partial x_j}+\frac{\partial u_j}{\partial x_i}\right)
\end{equation*}

The deformation work terms $\overline{u_i u_j}S_{ij}$ occurs in both equations with opposite signs. That is the exchange of energy between the mean flow and the turbulence.

Viscous dissipation: $-2\nu\overline{s_{ij}s_{ij}}$, it is a drain of energy and could not be neglected.

\textbf{Production equals dissipation}

In a steady, homogeneous, pure shear flow, we have

\begin{equation*}
    -\overline{u_iu_j}S_{ij}=2\nu\overline{s_{ij}s_{ij}}
\end{equation*}

The rate of production of turbulent energy by Reynolds stresses euqals the rate of viscous dissipation. In most flows, this is not always true, but they are always of the same order of magnitude.

With scale relation, we can find

\begin{equation*}
    \overline{s_{ij}s_{ij}}\gg S_{ij} S_{ij}
\end{equation*}

When the Reynolds number is large, the fluctuating strain rate is much larger than the mean rate of strain.

\textbf{Taylor microscale}

In isotropic turbulence, the dissipation rate

\begin{equation*}
    \epsilon=2\nu\overline{s_{ij}}s_{ij}=15\nu\overline{\left(\partial u_1/\partial x_1\right)^2}
\end{equation*}

We define a new length scale $\lambda$ (Taylor microscale) by

\begin{equation*}
    \overline{\left(\partial u_1/\partial x_1\right)^2}=\frac{\overline{u-1}}{\lambda^2}
\end{equation*}

Then

\begin{equation*}
    \epsilon=15\nu\mathcal{u}^2/\lambda^2
\end{equation*}

If $S_{ij}$ is of order $\mathcal{u}/\ell$ and $-\overline{u_i u_j}$ is of order $\mathcal{u}^2$, then

\begin{equation*}
    \mathcal{A}\mathcal{u}^3/\ell=15\nu\mathcal{u}^2/\lambda^2
\end{equation*}

Thus

\begin{equation*}
    \frac{\lambda}{\ell}=\left(\frac{15}{\mathcal{A}}\right)^1/2 R_\ell^{-1/2}
\end{equation*}

Where $\mathcal{A}$ is an undetermined constant, presumably of order one. We know that the Taylor microscale is always much smaller than the integral scale.

\textbf{Scale relations}

The smallest scale is the Kolmogorov microscale $\eta$

\begin{equation*}
    \eta=(\nu^3/\epsilon)^1/4
\end{equation*}

The relation between $\ell$, $\lambda$ and $\eta$

\begin{align*}
    \frac{\lambda}{\ell}&=\frac{15}{\mathcal{A}}R_\lambda^{-1}\\
    \frac{\lambda}{\eta}&=15^{1/4}R_\lambda^1/2
\end{align*}

Where $R_\lambda=\mathcal{u}\lambda/\nu$ is called the microscale Reynolds number.

\textbf{Sectral energy transfer}

If there is only one charateristic length $\ell$, the dissipation rate can be estimated as

\begin{equation*}
    \epsilon=\mathcal{A}\mathcal{u}^3/\ell
\end{equation*}

Considering the production $\mathcal{P}$ and dissipation $\epsilon$

\begin{equation*}
    -\overline{u_iu_j}S_{ij}\sim\mathcal{A}\mathcal{u}^3/\ell
\end{equation*}

\textbf{Further estimates}

The pressure-work term

\begin{equation*}
    -\frac{\partial}{\partial x_j}\left(\frac{1}{\rho}\overline{u_j p}\right)\sim\frac{\mathcal{u}^3}{\ell}
\end{equation*}

Mean transport of turbulent energy by turbulent motion

\begin{equation*}
    -\frac{\partial}{\partial x_j}\left(\frac{1}{2}\overline{u_iu_iu_j}\right)\sim\frac{\mathcal{u}^3}{\ell}
\end{equation*}

Transport by viscous stresses

\begin{equation*}
    2\nu\frac{\partial}{\partial x_j}\sim\frac{\mathcal{u}^3}{\ell}R_l^{-1}
\end{equation*}

\textbf{Wind-tunnel turbulence}

Nearly homogeneous turbulence in a low-speed wind tunnel.

Choose $U_1$ as the only non-zero component of the mean velocity.

\begin{equation*}
    U_1\frac{\partial}{\partial x_1}\left(\frac{1}{2}\overline{u_iu_i}\right)=-\frac{\partial}{\partial x_1}\left(\frac{1}{\rho}\overline{u_1p}+\frac{1}{2}\overline{u_iu_iu_1}\right)-\epsilon
\end{equation*}

We assume that $R_\ell$ is large, the viscous transport term can be neglected.

\begin{equation*}
    U_1\frac{\partial}{\partial x_1}\left(\frac{1}{2}\overline{u_iu_i}\right)=\mathcal{O}\left(\frac{U_1}{x_1}\mathcal{u}^2\right)
\end{equation*}

\begin{equation*}
    -\frac{\partial}{\partial x_1}\left(\frac{1}{\rho}\overline{u_1p}+\frac{1}{2}\overline{u_iu_iu_1}\right)-\epsilon=\mathcal{O}\left(\frac{\mathcal{u}^3}{x_1}\right)
\end{equation*}

\begin{equation*}
    \epsilon=\mathcal{O}\left(\frac{\mathcal{u}^3}{\ell}\right)
\end{equation*}

In grid turbulence, velocity fluctuations are small: $\mathcal{u}\ll U$. Thus,

\begin{equation*}
    U_1\frac{\partial}{\partial x_1}\left(\frac{1}{2}\overline{u_iu_i}\right)=-\epsilon
\end{equation*}

And dimensionally,

\begin{equation*}
    \frac{U_1}{x_1}=C\frac{\mathcal{u}}{\ell}
\end{equation*}

Which suggest that the time scale of the flow is of the same order of the time scale of the turbulence.

The change of $\ell$ and $\mathcal{u}$ downstream is omitted here.

\textbf{Pure shear flow}

Omitted here.

\subsection{Vorticity dynamics}

What do we mean by saying that turbulence is rotational and dissipative

\textbf{Vorticity vector and rotation tensor}

The vorticity is the curl of the velocity vector:

\begin{equation*}
    \tilde{\omega_i}=\epsilon_{ijk}\frac{\partial \tilde{u_k}}{\partial x_j}
\end{equation*}

$\epsilon_{ijk}$: Levi-Civita notation, $\epsilon_{123}=\epsilon_{231}=\epsilon_{312}=1$, $\epsilon_{321}=\epsilon_{132}=\epsilon_{213}=-1$.

The deformation rate can be split into two parts: symmetric and skew-symmetric part.

\begin{equation*}
    \frac{\partial\tilde{u_i}}{\partial x_j}=\tilde{s_{ij}}+\tilde{r_{ij}}
\end{equation*}

Symmetric: strain rate

\begin{equation*}
    \tilde{s_{ij}}=\frac12\left(\frac{\partial \tilde{u_i}}{\partial x_j}+\frac{\partial \tilde{u_j}}{\partial x_i}\right)
\end{equation*}

Skew-symmetric: rotation tensor

\begin{equation*}
    \tilde{r_{ij}}=\frac12\left(\frac{\partial \tilde{u_i}}{\partial x_j}-\frac{\partial \tilde{u_j}}{\partial x_i}\right)
\end{equation*}

The vorticity vector is related only to the skew-symmetric part

\begin{equation*}
    \tilde\omega_i=\epsilon_{ijk}\tilde{r_{kj}}
\end{equation*}

And

\begin{equation*}
    \tilde{r_{ij}}=-\frac12\epsilon_{ijk}\tilde{\omega_k}
\end{equation*}

\textbf{Vortex terms in the equations of motion}

Omitted here.

\textbf{Reynolds stress and vorticity}

Decompose the vorticity $\tilde{\omega_i}$

\begin{equation*}
    \tilde{\omega_i}=\Omega_i+\omega_i,\quad\overline{\omega_i}=0
\end{equation*}

The equation for the mean velocity $U_i$

\begin{equation*}
    0=-\frac{\p}{\p x_i}\left(\frac{P}{\rho}+\frac12U_jU_j+\frac12\overline{u_ju_j}\right)+\epsilon_{ijk}\left(U_j\Omega_k+\overline{u_j\omega_k}\right)+\nu\frac{\p^2U_i}{\p x_j \p x_j}
\end{equation*}

Since $\overline{u_ju_j}\ll U_jU_j$, and we consider such a two-dimensional flow that $U_1\gg U_2$, $U_3=0$, $\p/\p x_1\ll\p/\p x_2$, also neglect the viscous term and the contribution of the turbulence,

\begin{equation*}
    U_1\frac{\p U_1}{\p x_1}+U_2\frac{\p U_1}{\p x_2}=-\frac{1}{\rho}\frac{\p P}{\p x_1}+\overline{u_2\omega_3}-\overline{u_3\omega_2}
\end{equation*}

For the Reynolds shear stress $-\overline{u_1u_2}$,

\begin{equation*}
    \frac{\p}{\p x_2}\left(-\overline{u_1 u_2}\right)=\overline{u_2\omega_3}-\overline{u_3\omega_2}
\end{equation*}

\textbf{The vorticity equation}

Taking curl operator to the Navier-Stokes equation ($\epsilon_{pqi}\p/\p x_q$), and some analysis,

\begin{equation*}
    \frac{\p \tilde{\omega}_p}{\p t}=\tilde{\omega}_k\frac{\p \tilde{u}_p}{\p x_k}-\tilde{u}_k\frac{\p \tilde{\omega}_k}{\p x_k}-\nu\frac{\p}{\p x_p}\left(\frac{\p \tilde{\omega}_k}{\p x_k}\right)+\nu\frac{\p^2\tilde{\omega}_p}{\p x_k \p x_k}
\end{equation*}

The first viscous term

\begin{equation*}
    \frac{\p \tilde{\omega}_k}{\p x_k}=\epsilon_{ijk}\frac{\p^2\tilde{u}_j}{\p x_i\p x_k}=0
\end{equation*}

Thus, finally

\begin{equation*}
    \frac{\p \tilde\omega_i}{\p t}+\tilde u_j\frac{\p\tilde\omega_i}{\p x_j}=\tilde\omega_j\frac{\p\tilde u_i}{\p x_j}+\nu\frac{\p^2\tilde\omega_i}{\p x_j\p x_j}
\end{equation*}

Note that the skew-symmetric part $\tilde r_{ij}$ does not contribute to the equation, the equation could be further simplified as

\begin{equation*}
    \frac{\p \tilde\omega_i}{\p t}+\tilde u_j\frac{\p\tilde\omega_i}{\p x_j}=\tilde\omega_j\tilde s_{ij}+\nu\frac{\p^2\tilde\omega_i}{\p x_j\p x_j}
\end{equation*}

\textbf{Vorticity in turbulent flows}

\begin{equation*}
    U_j\frac{\p \Omega_i}{\p x_j}=-\overline{u_j\frac{\p\omega_i}{\p x_j}}+\overline{{\omega_j} s_{ij}}+\Omega_jS_{ij}+\nu\frac{\p^2\Omega_i}{\p x_j\p x_j}
\end{equation*}

The mean vorticity and fluctuating vorticity are divergenceless

\begin{equation*}
    \frac{\p\Omega_i}{\p x_i}=0,\qquad\frac{\p\omega_i}{\p x_i}=0
\end{equation*}

Continuity:

\begin{equation*}
    \frac{\p u_i}{\p x_i}=0
\end{equation*}

We have

\begin{align*}
    \overline{u_j\frac{\p\omega_i}{\p x_j}}&=\frac{\p}{\p x_j}\left(\overline{u_j\omega_i}\right)\\
    \overline{{\omega_j} s_{ij}}&=\frac{\p}{\p x_j}\left(\overline{\omega_j u_i}\right)
\end{align*}

The first term is a transport ``divergence'', while the second term is the gain of mean vorticity caused by the stretching and rotation of fluctuating voriticity components by fluctuating strain rates.

\textbf{Two-dimensional mean flow}

\textbf{The dynamics of $\Omega_i\Omega_i$}

\textbf{The equation for $\overline{\omega_i\omega_i}$}

\textbf{Turbulence is rotational}

\textbf{An approximate vorticity budget}

\textbf{Multiple length scales}

\textbf{Stretching of magnetic field lines}

\subsection{The dynamics of temperature fluctuations}

\begin{equation*}
    U_j\frac{\p}{\p x_j}\left(\frac12\overline{\theta^2}\right)=-\frac{\p}{\p x_j}\left[\frac12\overline{\theta^2u_j}-\gamma\frac{\p}{\p x_j}\left(\frac12\overline{\theta^2}\right)\right]-\overline{\theta u_j}\frac{\partial \Theta}{\p x_j}-\gamma\overline{\frac{\p\theta}{\p x_j}\frac{\p\theta}{\p x_j}}
\end{equation*}

For steady homogeneous shear flow

\begin{equation*}
    -\overline{\theta u_j}\frac{\p \Theta}{\p x_j}=\gamma\overline{\frac{\p \theta}{\p x_j}\frac{\p \theta}{\p x_j}}
\end{equation*}

\textbf{Microscales in the temperature field}

Let us define

\begin{equation*}
    \overline{\left(\frac{\p\theta}{\p x_1}\right)^2}=2\frac{\overline{\theta^2}}{\lambda_\theta^2}
\end{equation*}

Then the isotropic temperature field has

\begin{equation*}
    \gamma\overline{\frac{\p \theta}{\p x_j}\frac{\p \theta}{\p x_j}}=6\frac{\overline{\theta^2}}{\lambda_\theta^2}
\end{equation*}

With order analysis we obtain

\begin{equation*}
    \frac{\lambda_\theta}{\lambda}=C\left(\frac{\gamma}{\nu}\right)^{1/2}
\end{equation*}

$C$ is of order one.

\dots

\textbf{Buoyant convection}

\textbf{Richardson numbers}

\textbf{Monin-Oboukhov length}

\textbf{Convection in the atmospheric boundary layer}



\ifx\allfiles\undefined         %独立编译
\end{document}
\fi